---
title: "clustering gating by kmeans"
author: "mike"
date: "6/26/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

This document demonstrates how to use `openCyto` plugin mechanism to incorporate the clustering-based gating algorithm into `openCyto` auto-gating framework. 

## Prepare the data
```{r}
library(flowCore)
library(flowWorkspace)
dataDir <- system.file("extdata",package="flowWorkspaceData")
gs <- load_gs(list.files(dataDir, pattern = "gs_manual",full = TRUE))
#simplify gating tree
gs_pop_remove(gs, "CD4")
gs_pop_remove(gs, "CD8")
plot(gs)
```

## Write a custom gating function that runs kmeans and wrap the result as a `multipleFilterResult`
```{r}
kmeans_gating <- function(fr, pp_res = NULL, channels, ...){
	kmeans_results <- kmeans(exprs(fr)[,channels], ...)
	res <- as.factor(kmeans_results$cluster) 
	#name the sub pops properly
	levels(res) <- paste("tsub", levels(res))
	#return it as multipleFilterResult object
	as(res, "filterResult")
	
}
```

## test it to ensure it returns the expected result
```{r}
gh <- gs[[1]]
fr <- gh_pop_get_data(gh, "CD3+")
markers <- c("CD4", "CD8", "CD3")
channels <- sapply(markers, function(marker){
  getChannelMarker(fr, marker)$name
})

kmeans_gating(fr, channels = channels, centers = 3)
```
Note that the `levels` of the `factor` will be used to tag the clustering population names.

## Register it as plugin
```{r}
library(openCyto)
register_plugins(fun = kmeans_gating, methodName = "tsub_gating")
```

## Use it in openCyto gating
```{r}
gs_add_gating_method(gs
					 , alias = "*" #* means the pop names are parsed from gating results
					 , pop = "*"
					 , parent = "CD3+"
					 , dims = "CD4,CD8,CD3" #channels to be passed to gating function
					 , gating_method = "tsub_gating"
					 , gating_args = "centers=3" #arguments passed on to gating function
					 )

```

## Visualize the result
```{r}
plot(gs)
library(ggcyto)
gs_pop_get_stats(gs, node = c("CD3+", "tsub 1", "tsub 2", "tsub 3"))
ggcyto(gs, aes(cd4, cd8), subset = "CD3+") + geom_gate("tsub 1", color = "red") + geom_gate("tsub 2", color = "blue") + geom_gate("tsub 3", color = "black")
```

